\documentclass[a4paper]{article}

\usepackage{urdu-prose}
\usepackage{enumerate}

% Increse size of page number in bottom
\usepackage{fancyhdr}
\fancypagestyle{plain}{%
	\fancyhf{}
	\fancyfoot[C]{\LARGE\thepage}
	\renewcommand{\headrulewidth}{0pt}
	\renewcommand{\footrulewidth}{0pt}
}
\pagestyle{plain}

% A macro for placing italicizes English intructions on the left
\newcommand{\instr}[1]{\vm\hfill\en{\itshape #1}}


\begin{document}

\begin{center} \Huge
	Shoaib Skit
\end{center}

\startUrdu

	sYn 1987 ki aik snori xam, xor laowr miN aik gHrany miN aik lRka pida owa js ky waldin ny aPs ka nam xeib rkHa.
	aPs ki gwlaUi ka crca gli gli miN tHa.
	hta ko io Kbr tin priwN tk ponci jw aIs bcy kw dikHny AUiN.

	\begin{itemize}
		\idialog[4em]{poli pri}{aPf kwUi bco atna gwl kisy ow skta oy?}
		\idialog[4em]{dwsri pri}{miN aIsy kHa jaUwN gi.}
		\idialog[4em]{tisri pri}{aIsy kHany sy botr oy om tinwN aIsy aik aik thfo dy diN}
		\dialog[4em]{poli dw priaN}{oaN io THik oy.}
		\idialog[4em]{poli pri}{miri dea oy ko tmoari xkl dlip kmar jisi awr bal xao rPK Kan jisy owN.}
	\end{itemize}

	xaUd io aIsi dea ka aCr tHa ko or sal grmiwN miN xeib ki aYmi aPs ky bal awr gHny krny ky liy xeib kw gnja kra diti tHiN.

\instr{Show picture of bald Shoaib.}

\dialog[4em]{dwsri pri}{miri dea oy ko tmoari \en{bowling} wsim akrm ki vrh ow.}

\newpage
\instr{Suddenly the witch appears, cackling.}

\vm
\begin{itemize}
	\idialog{cRil}{oa oa oa. miN bHi aIs bcy kw dea dwngi}
	\idialog{priaN}{noiN!!!}
	\idialog{cRil}{oaN. miri dea oy ko io bco omixo apni ciziN gmata roy. oa oa oa.}
	\idialog[4em]{tisri pri}{xeib miN tmoari ciziN gmny sy tw noiN bca skti. mgr miri io dea oy ko km aYz km tmoara \en{wallet} omixo tmoary pas waps A jaUy.}
\end{itemize}

	awr ksi ky bary miN iqin sy kcH noiN koa ja skta likn xeib io Jrwr smjHta Aia oy oy ky io tmam deaUiN pwri ow gUiN.

\vm
\rule{\textwidth}{1pt}
\vm

	xeib ka bcpn onsty kHilty, pRHty lkHty,  kHaty pity awr \en{VCR} pr aYn gInt dfeo \en{Aladdin} dikHty owUy gzr roa tHa ky acank 1996 miN xeib kw mhbt ow gUi.

\instr{Play song: I am in love.}

	io iqina~ dwsri pri ki dea ka ntijo tHa kiwN ky xeib ny apny Ap kw wsim akrm ky exq miN grftar paia.

	bawjwd aIs ky ko xeib acHi KaSi \en{Leg Break bowling} krata tHa ab aPs kw iqin ow gia ko wo aik \en{right-handed} wsim akrm oy.
	aIs bat miN Zra brabr scaUi noiN tHi.

\dialog{ebas}{xeib, \en{toss} kr lw.}

\begin{enpara}
	\itshape
	Shoaib closes his fists, crosses them, and presents them to Abbas

	Abbas picks his eye-lashes, counts them on either hand, and slaps Shoaib's right fist which he opens.
\end{enpara}

	\vspace{0\baselineskip}
	\begin{itemize}
		\idialog{ebas}{jit gUy. om poly \en{batting} kringy.}
		\idialog{xeib}{\en{Please} eabd bHaUi mjHy pola \en{over} krany diN.}
		\idialog{eabd}{likn tm ny poli \en{batting} bHi tw ki tHi}
		\idialog{xeib}{\en{Pleeeaase}. mjHy pta oy miN aInoiN \en{out} kr dwnga}
		\idialog{eabd}{acHa bHUi THik oy. likn aik xrv pr. tm \en{fast bowling} noiN kraUw gy.}
		\idialog{xeib}{kia? Ap dikHiN miN anoiN kisy \en{out} krta owN apni \en{fast bowling} sy}
	\end{itemize}

	awr pHr xeib kw Kwb mar pRti tHi jb tk ky wo mjbwra~ \en{spin} pr tbdil noiN ow jata tHa.

\vm
\rule{\textwidth}{1pt}
\vm\vm

	jb xeib 16 sal ka owa tw aPs ka Kandan amriko mntql ow gia.
	amriko jany sy aPs ki zndgi pr sb sy bRa aCr io pRa ko joaN wo gHr ky bny owUy \en{french fries}, papR awr Am kHata tHa wo ab \en{chips}, \en{coke}, awr \en{pizza} kHany lga js ky ntijy miN wo ansan km awr aik antoaUi mwTi bli ziado lgny lga.

\begin{enpara}
	\itshape
	Dania, Aiman and Alina walk across the stage holding placards for the three foods, then flip the placards and walk back across showing the american variants. At the end show Shoaib's fat-cat picture followed by playing the Wain-wain sound from KKKG.
\end{enpara}

\rule{\textwidth}{1pt}
\vm\vm\vm

	\en{High-school} Ktm krny ky bed xeib ka daKlo amriko ki aik mxowr \en{university} miN ow gia.

\instr{Pause here and Play Dark Knight Theme (uplifting)}

	\vspace{0.5\baselineskip}
	woaN poncty oi xeib \en{Chicago} ka diwano ow gia.
	wo or jgo \en{Chicago} ky gPn gata.

\begin{itemize}
	\idialog[3.5em]{xeib}{io bHi kwUi srdi oy. \en{Chicago} miN rony ky bed tw miN ioaN nnga sw skta owN.}
	\idialog[3.5em]{\en{Random}}{bHaUi miN tw Srf Apka \en{wallet} waps krny Aia owN. io liN.}
\end{itemize}

\instr{Play teri galiyan and show slide-show of Chicago pictures}

	\vspace{0.5\baselineskip}
	dnia tw io smjH roi tHi ko lRka \en{Bio-chemistry} pRH roa oy likn hqiqt miN xeib ki krkT sy mhbt miN dn bdn aJafo owta ja roa tHa.

	Kwari ka io ealm tHa ko aPs zmano miN \en{University of Chicago} ky \en{Indoor Basket-ball Court} awr \en{Ice Rink} miN \en{basket-ball} awr \en{ice hockey} ky bjaUy xeib by antoa snjidgi ky satH krkT kHilty owUy awr dwsry kHlaRiwN ky satH lRty owUy paia jata.

	ioaN tk ky krkT ka exq aPsy kHinc kr \en{St. Lucia} tk ly gia.

\instr{Show pictures of St. Lucia.}

	awr jb exq sca ow tw mhbwb ka didar nsib ow oi jata oy.

\instr{Pictures with Afridi and co.}

\vm
\rule{\textwidth}{1pt}
\vm

	dn rat krkT kHilna, dikHna, \en{discuss} krna, zndgi aIsi ka nam tHa.
	aIsi lUy jb xeib \en{graduate} owa tw aPs ka dl \en{bio-chemistry} miN ziado dir noiN lg ska.

	bot Zoni kx mkx miN mbtla rony ky bed wo \en{job} cHwR kr \en{Sri Lanka} miN \en{World Cup} dikHny cla gia.

	aPs ky bed xeib ka THkana mlna mxkl ow gia.
	wo kbHi \en{New Zealand} miN \en{cricket coaching} sikH roa owta tw kbHi \en{Australia} miN \en{Masters in Sports Management} krta owa paia jata.

	awr pHr acank Kbr Ati ko brKwrdar \en{Pacific} kwd kr woi \en{Masters Washington DC} miN mkml kr roy oiN. 

\begin{enpara}
	\itshape
	Play behti hawa sa thaa wo\\
	Show Shoaib hopping around on a map
\end{enpara}

\vp
	satH satH cnd om Kial sYr pHIrwN ky satH \en{Pace is Pace Yaar} ky nam sy aik \en{podcast} xrwe kr dia.

\instr{Show screen-capture from one of the episodes and play PTV cricket music}

	Aosto Aosto Kwd xeib kw awr baqi dnia kw ahsas ow gia ko aYb \en{career} krkT miN oi owga.

\rule{\textwidth}{1pt}
\vm\vm

	apna \en{Masters} ka \en{Thesis} oatH miN pkRy, dl miN sci aPmng lUy xeib pakstan miN warId ow gia.

\instr{Show video clip of SRK jumping out of helicopter in KKKG}

	sYpna tHa ko pakstani krkT ky bHag kHwl dwnga.
	aIs Kwaox ki tkmil ki Kavr xeib \en{PCB} ponc gia joaN aPs ki \en{Najam Sethi} sy mlaqat kcH iwN owUi: 

\instr{Play face-mapped clip from Seinfeld: Hire this man}

	\en{PCB} miN xeib ny apna sr diwarwN miN mar mar kr AKr kar diwarwN kw twR Dala awr \en{PSL} kw hqiqt bna dia.

\instr{Show picture(s) of Shoaib at the PSL and Isb Utd lifting the trophy.}

	\en{PSL} ka aIfttah kr liny ky bed xeib ny \en{Franchises} ki vrf rPK kia awr \en{Islamabad United} miN \en{COO} bHrti ow gia.

	\begin{itemize}
		\idialog[3.5em]{\en{Random}}{\en{Excuse me} bHaUi. io xaUd Apka \en{wallet} mjHy gra owa mla oy. Ap kw miN ny \en{PSL} ky dwran \en{presentation ceremony} miN dikHa tHa.}
		\idialog[3.5em]{xeib}{dikHa ow ga. miN tw aItni \en{parties} jata owN.}
	\end{itemize}

\rule{\textwidth}{1pt}

	xeib io noiN janta tHa ko io "tqdir" tHi jw aPs kw \en{Islamabad United} ly AUi tHi joaN pr kwUi, no janty owUy, aPs ka antVar kr roa tHa.

\begin{enpara}
	\itshape
	\begin{enumerate}[(i)]
		\item Shoaib walking in from one side typing on his phone and muttering.
		\item Amna walking in from the other side with her hands filled with wrapping papers, tapes and decoration items talking to someone.
	\end{enumerate}
\end{enpara}

\vspace{0\baselineskip}
	\begin{itemize}
		\idialog{Amno}{oaN bHUi Amno eli bwl roi owN. \en{Leisure Club} sy \en{meeting} prswN rkH lw. awr mira \en{Mighty Zinger} kdHr oy?}
	\end{itemize}

\begin{enpara}
	\itshape
	\begin{enumerate}[(i)]
		\item They bump in to each other with the decoration items falling down.
		\item They both kneel down to pick up the fallen things. Shoaib gazes at Amna, who is more occupied with picking up her things.
		\item Amna ignores Shoaib and walks away.
		\item Shoaib stares after Amna with his mouth hanging open.
	\end{enumerate}
\end{enpara}

\vspace{\baselineskip}
\begin{enpara}
	\itshape
	Play "chalte chalte younhi" uptill 1:12

	Choreography:
	\vm
	\begin{enumerate}
		\item Zain moves to the center of the stage and stands with his arms raised.
		\item When music crescendos the girls run in with trailing dupattas.
		\item When whistling starts girls run off and the boys walk in dancing.
		\item During the vocals only one boy is dancing for each line while the others are frozen.
		\item When the female vocals start the boys walk off and the girls stroll past signing at Zain.
		\item At the end Zain is still standing frozen.
	\end{enumerate}
\end{enpara}

\vp
acank xeib ky dIl miN krkT awr \en{phone} ki jgo ksi awr ny ly li tHi.

\instr{Play: What is mobile number (uptil 1:18)?}

\begin{enpara}
	\itshape
	Choreography:
	\vm\vm
	\begin{enumerate}
		\item Amna walks around ignoring Shoaib. 
		\item At end Amna walks past Shoaib ignoring him.
	\end{enumerate}
\end{enpara}

\vz
\begin{itemize}
	\idialog{xeib}{kwn oy io jIs ny PmR kr xeib kw noiN dikHa?}

	\idialog{Amno}{\en{Minus} \hfill \en{\itshape Play wain-wain from KKKG}}
\end{itemize}

bdqsmti sy Amno xeib ky bary miN aik cHwTi si Glv fomi ka xkar tHi.

\vp
\instr{Amna passes by and stops to pick it up Shoaib's wallet.}

\dialog{Amno}{xeib ka \en{wallet}? \en{Oooh} aIs miN tw aPn ky bcwN ki tSwiriN owngi.}

\vp
\instr{Amna opens the wallet (in search of the pictures) but instead finds her own.} 

	\dialog{Amno}{miri tSwir?}

\begin{enpara}
	\itshape
	\begin{enumerate}
		\item Show Amna's picture on projector with zooms and negatives.
		\item Play Indian Soap Opera music.
		\item Amna walks over to Shoaib and hesitantly hands over the wallet.
	\end{enumerate}
\end{enpara}

\vz
\vp
\begin{itemize}
	\idialog{Amno}{miN tw smjH roi tHi ko Ap xadi xdo oiN. awr Ap ky dw bcy bHi oiN. Ap ki xadi noiN owUi owUi oy?}
	\idialog{xeib}{noiN. balkl noiN. likn agr tPm ...}
\end{itemize}

\begin{enpara}
	\itshape
	\begin{enumerate}
		\item Amna turns away from Shoaib and thinks to herself.
		\item The actors walk off stage to be replaced by the actual couple.
		\item A voice-over is provided for Amna's thoughts.
	\end{enumerate}
\end{enpara}

\vp
\dialog{Amna}{Ap sy xadi? Ap ky bal xao rK Kan sy tw mlty oiN. awr \en{bowling} bHi balkl wsim bHaUi jisi oy. likn apni cizwN ky bary miN bot by prwao oiN, or wqt aPnoiN kHwty roty oiN. pr \en{wallet} omixo waps A jata oy.}

\dialog{Amna}{\en{I Laike it.}}

\instr{Amna turns to Shoaib and blushes}

\vm
\dialog{Amno}{mjHy qbwl oy.}

\vm
\hfill\en{\itshape Play ``Power of Love"}

\end{document}
